Type-Safe Modular Parsing

### 2017-09-05 SLE_17/sections/RelatedWork.tex
Change code font size.
Improve text on wyvern

@@

Besides, type-specific languages~\cite{omar14} do support
separate compilation and type safety. The modularity of parsing is incorporated in its elaborated type
system. Whereas our approach does not rely on an extension to semantics, but simply uses a pattern
that is applicable in mainstream OO languages, where the type system ensures
type safety.

>>>>

\paragraph{Safely Composable Type-Specific Languages} There is almost no work on 
semantically modular parsing. A notable exception is the work 
on safely composable type-specific languages~\cite{omar14}. In this
work the extensible language Wyvern supports the addition of new
syntax and semantics, while preserving type-safety and separate
compilation. However this approach and our work have different goals: 
their approach is aimed at supporting extensibility of Wyvern with
new syntax; whereas our approach is a general technique aimed at 
modular parsing of any languages. In contrast to their modular parsing 
approach, which is directly built-in to the Wyvern language, our approach is 
library-based and can be used by many  mainstream OO languages.

\begin{comment}
Besides, type-specific languages do support
separate compilation and type safety. The modularity of parsing is incorporated in its elaborated type
system, allowing users to introduce new syntax. Whereas our approach does not rely on an extension to semantics, but simply uses a pattern
that is applicable in mainstream OO languages, where the type system ensures
type safety.
\end{comment}

@@
